Tina Paper In Development

### 2024-10-30 docs/writing/paper.tex
I think I figured out the intro of the outline now. Writing in the paper is almost caught up

\section{Introduction}
The study of tree rings has proven useful across multiple fields, proving to be a reliable subject for reconstructing past climates of regional and local environments, as well as a mechanism to understand tree growth response \citep{fritts_dendroclimatology_1971} \citep{williams_using_2010} \citep{guibal_dendrochronology_2021} \citep{sheppard_dendroclimatology_2010}.
To obtain these data from the tree rings, it is necessary to measure tree rings from a tree cookie or core. The first high precision tool for this purpose was a stage micrometer, involving a trained technician to incrementally shift a tree core under the objective of a microscope - informing a computer when a new ring is encountered \citep{robinson_microcomputer_nodate}.
While this method has very high precision, the data is only as accurate as the experience and knowledge of the technician at the time of recording \citep{levanic_atrics_2007}.
The desire to remove repetition of errors in sampling and sampling bias across to individual technicians led researchers to an alternative - image analysis. 
\par
The first step in measuring tree ring width from images requires the digitization of the sample. There are currently two competing models to digitize a sample. The first model is to use a flatbed scanner or similar tool, providing the benefit to

The first approach involved flatbed scanning technology which digitized the surface of a prepared sample \citep{guay_new_1992}. 
Flatbed scanners eventually encountered a resolution insufficiency when analyzing very narrow tree rings on the scale of a few cells. A new method introduced with the ATRICS system increased the resolution of samples by stitching together multiple images from a digital microscope camera \citep{levanic_atrics_2007}. 
ATRICS set an example of the process which has been implemented in two other image acquisition tools, Gigapixel and CaptuRING \citep{griffin_gigapixel_2021, garcia-hidalgo_capturing_2022}.
Both of these tools use professional cameras to take individual images of cores, although CaptuRING requires the technician to transfer the images to a second device and use the proprietary image stitching software PTGUI. 
A budget friendly image acquisition tool with integrated image stitching for both cores and cookies has yet to be released.

% Potentially should have a section on tree ring width measurement software
% The images were then fed to software such as WinDENDRO to have technicians click tree rings on a graphical user interface (GUI) \citep{guay_new_1992}.
% More modern implementations of measurement software now exists which includes width measurement, cross dating, and autodetection of rings as well \citep{maxwell_measuring_2021}.

>>>>

\section{Introduction}
The study of tree rings has proven useful across multiple fields, proving to be a reliable subject for reconstructing past climates of regional and local environments, as well as a mechanism to understand tree growth response \citep{fritts_dendroclimatology_1971} \citep{williams_using_2010} \citep{guibal_dendrochronology_2021} \citep{sheppard_dendroclimatology_2010}.
To obtain these data from the tree rings, it is necessary to measure tree rings from a tree cookie or core. The first high precision tool for this purpose was a stage micrometer, involving a trained technician to incrementally shift a tree core under the objective of a microscope - informing a computer when a new ring is encountered \citep{robinson_microcomputer_nodate}.
While this method has very high precision, the data is only as accurate as the experience and knowledge of the technician at the time of recording \citep{levanic_atrics_2007}.
The desire to remove repetition of errors in sampling and sampling bias across to individual technicians led researchers to an alternative - image analysis. 
\par
The first step in measuring tree ring width from images requires the digitization of the sample. There are currently two competing models to digitize a sample. The first model is to use a flatbed scanner or similar tool, to digitize the entire sample at once \citep{guay_new_1992}.
Eventually flatbed scanners have reached a maximum resolution, introducing the second model spawning from ATRICS \citep{levanic_atrics_2007}. A high resolution camera takes multiple images across the surface of the sample, and uses image stitching techniques to combine them into one ultra high resolution image \citep{muhlich_stitching_2022}.
This methodology is often seen in other fields such as mineralogy and cellular biology \citep{ro_image_2021,mohammadi_fast_2024}.

Both of these tools use professional cameras to take individual images of cores, although CaptuRING requires the technician to transfer the images to a second device and use the proprietary image stitching software PTGUI. 
A budget friendly image acquisition tool with integrated image stitching for both cores and cookies has yet to be released.
